---
title: "Homework 9"
author: "Ze Zheng"
date: "4/15/2021"
output: pdf_document
---



\section{Economic Model}
The employment level of sales and office occupations and the employment level of agriculture and related industries. We believe that if agriculture sector improves in their output then the sales department will sell more agriculture and thus will improve profits on the office level side which then it would crate more vacancies in the job market because a firm will have more capital to hire more people. We will be doing a cointergration on these two different random walks.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(readxl)
library(knitr)
library(forecast)
library(tseries)
library(urca)
library(stargazer)
library(ggthemes)
library(tidyverse)
library(vars)
library(ggplot2)
```



```{r Plot between total IRAs and Real GDP, echo=FALSE}
FarmSales <- read_excel("FarmSales.xls")


ggplot(FarmSales)+
  geom_line(aes(x=Month, y=Sales), color="red")+
  geom_line(aes(x=Month, y=Farm), color = "blue")+
  labs(x= "Month", y="Employment Level")
#$\tau_\tau$ = 2.8908 less than 3.42 Fail to Reject Move to $H_{0,2}$
#$\phi_3$ =4.2423 less than 6.30 Fail to reject Move to $H_{0,5}$
#$\tau_2$ =0.7831 less than 2.87  Fail to reject Move to $H_{0,6}$
#$\phi_1$ =0.4217  less than 4.61 Fail to reject Move to $H_{0,9}$
#$\tau$ = 0.5065 less than 1.95 Fail to reject Pure Random Walk I(1)
   
```

\section{Anaylsis and Results}
First we did the Dicky Fuller test on both variables so that we could determine if it was a unit root of I(1). Both employment level - sales and office occupations and employment level - agriculture and related industries were series that appear to have a unit root of I(1) which is a pure random walk. Since both are pure random walk we will run a linear regression between the two variables to see if the two variables have any relation between each other. We got a $R^2$ of 0.019 and our t statistic for sales was -2.711 which already show us that there is not a relationship between the two variables. But we will also do a integration test by testing the $\hat{u}_t$ which we was made into a variable by taking the residual of the linear regressed variables of Sales and office occupations and agriculture and related industries. Then we use the Dicky Fuller test we tested the $\tau$ variable to decided it the variable was stationary or non-stationary. Though analysis we found the value of the test statistic was 1.3448. Which was less than critical value 1.95 meaning that $\hat{u}_t$ fails to reject the null hypothesis. Therefore this dictates that value is non stationary and the two variable do no cointergrate. 


```{r Fuller Dickey Test to see if Employment Level - Sales and Office Occupations is a I(1), include=FALSE}

summary(ur.df(FarmSales$Sales, type="trend", selectlags = "AIC", lags=36))
summary(ur.df(FarmSales$Sales, type="drift", selectlags = "AIC", lags=36))
summary(ur.df(FarmSales$Sales, type="none", selectlags = "AIC", lags=36))

#$\tau_\tau$ = 1.2917 less than 3.42 Fail to Reject Move to $H_{0,2}$
#$\tau_2$ =1.6342 less than 2.87  Fail to reject Move to $H_{0,6}$
#$\phi_1$ =1.6263  less than 4.61 Fail to reject Move to $H_{0,9}$
#$\tau$ = 1.0521 less than 1.95 Fail to reject Pure Random Walk I(1)

```




```{r Fuller Dickey Test to see if Employment Level - Agriculture and Related Industries is a I(1), include=FALSE}

summary(ur.df(FarmSales$Farm, type="trend", selectlags = "AIC", lags=36))
summary(ur.df(FarmSales$Farm, type="drift", selectlags = "AIC", lags=36))
summary(ur.df(FarmSales$Farm, type="none", selectlags = "AIC", lags=36))
```

```{r Testing for Cointergration, include=FALSE}
civ1<-lm(Farm~Sales,data=FarmSales)

stargazer(civ1,type="text", report=c("vcst"))

FarmSales$e1<-resid(civ1)

  
summary(ur.df(FarmSales$e1, type="none", selectlags = "AIC", lags=36))

```

```{r stuff,echo=FALSE}
ggplot(FarmSales)+
  geom_line(aes(x=Month, y=e1),color="red")+
  xlab("Date")+
  ylab("Residuals")+
  theme_minimal()
#$H_{0,10}$ = 1.3448 less than 1.95 meaning that $\hat{u}_t$ Fails to reject so it is non stationary and there is not a cointergration
```



